% Author: Pavol Loffay
% Project: Master thesis - Hawkular alert prediction
% Date 20.2.2015

\documentclass[12pt,oneside]{fithesis2}
% Packages
\usepackage[english]{babel}       % Multilingual support
\usepackage[utf8]{inputenc}       % UTF-8 encoding
\usepackage[T1]{fontenc}          % T1 font encoding
\usepackage[scaled=0.86]{berasans}
\usepackage[scaled=1.03]{inconsolata}
\usepackage[plainpages = false,pdfpagelabels]{hyperref}

\usepackage{multicol}

% my declared packages
% Images
\usepackage{graphicx}
\usepackage{float} 
% Math
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{commath} % abs
% Data structures, algorithms
\usepackage{listings}
\usepackage{algorithm} %algorithmix
\usepackage[]{algpseudocode} %noend
\lstset{language=java}

\usepackage{tabularx}
\usepackage{multirow}
\usepackage{pgf-pie}
%\definecolor{LightCyan}{rgb}{0.88,1,1}
%\usepackage{natbib} % for csplainnat.bib

% Url
\usepackage{url}
%\Urlmuskip=0mu plus 1mu
%\DeclareUrlCommand\url{\def\UrlLeft{<}\def\UrlRight{>} \urlstyle{tt}}

\usepackage{xparse}
\NewDocumentCommand{\INTERVALINNARDS}{ m m }{
    #1 {,} #2
}
\NewDocumentCommand{\interval}{ s m >{\SplitArgument{1}{,}}m m o }{
    \IfBooleanTF{#1}{
        \left#2 \INTERVALINNARDS #3 \right#4
    }{
        \IfValueTF{#5}{
            #5{#2} \INTERVALINNARDS #3 #5{#4}
        }{
            #2 \INTERVALINNARDS #3 #4
        }
    }
}

\newcommand{\ts}{\textsuperscript}
%\newcommand\nth{\textsuperscript{th}\xspace}

\hyphenation{data-bases}
\hyphenation{gar-bage}
\hyphenation{re-using}
\hyphenation{im-ple-men-ted}
\hyphenation{auto-cor-rel-a-tion}
\hyphenation{data-base}
\hyphenation{bench-marked}

\thesistitle{Alert Prediction in Metric Data Based on Time Series Analysis} % enter thesis title
\thesissubtitle{Master thesis}  
\thesisstudent{Bc. Pavol Loffay}    % name of the author
\thesiswoman{false}          % defines author’s gender  
\thesisfaculty{fi}  
\thesisyear{spring 2016}  
\thesisadvisor{RNDr. Adam Rambousek, Ph.D.} % fill in advisor’s name
\thesislang{en}                 % thesis is in English  

\begin{document}
\FrontMatter                    % The front matter
\ThesisTitlePage                % The title page
\begin{ThesisDeclaration}       % The declaration
  \DeclarationText
  \AdvisorName
\end{ThesisDeclaration}

\begin{ThesisThanks}            % The acknowledgements (optional)
  I would like to thank my supervisor RNDr. Adam Rambousek, Ph.D., Mgr. Jiri Kremser,
  family and Hawkular Team. Next, my thanks goes to Ing. Daniel Němec, Ph.D.
  for consulting theory behind time series analysis.

  Last but not least, I would like to thank to company Red Hat that provided me 
  with great opportunity to work on this project.
\end{ThesisThanks}

\begin{ThesisAbstract}          % The abstract
  The goal of the master's thesis is to develop a module for an open source monitoring
  and management platform Hawkular. The module should provide real time predictive capabilities for collected time
  series data. Proposed solution should be computationally efficient and more importantly, it should autonomously
  select the best time series model for given metric. In other words it should work without analyst's interaction.

  The master's thesis starts with time series theory and analysis of various approaches for time series forecasting. It
  discusses which models are best for Hawkular requirements. The implementation chapter focuses on the most important
  parts like time series models, automatic forecasters and integration into Hawkular. The last chapter conducts
  evaluation of the implemented models. Models are benchmarked against its alternatives from statistical language R.
  The results show that implemented models are similar to R alternatives from the prediction accuracy perspective.

\end{ThesisAbstract}

\begin{ThesisKeyWords}          % The keywords
  Time Series, Hawkular, Alert Prediction, Exponential Smoothing
\end{ThesisKeyWords}

\tableofcontents                % The table of contents
%   \listoftables                   % The list of tables (optional)
%   \listoffigures                  % The list of figures (optional)

\MainMatter                     % The main matter
\input{content}
\input{content2}

% Bibliography goes here
% Index goes here (optional)
\bibliographystyle{czplain}
%\bibliographystyle{csplainnat}
%\bibliographystyle{czechiso} % sets plain bibliography style
\bibliography{bibliography}     % BibTeX database file

% Appendix
\appendix
\input{appendix}

\end{document}
